SU($n$) ferromagnets near the Heisenberg point

### 2020-06-22 collective_sun/sun_perturbation.tex
added text describing truncated shell simulations

In order to simulate dynamics within excited-state manifolds, we first
need to classify the set of excited states, and construct a suitable
basis.  In the case of SU(2), a common starting point is to identify
states with a definite (non-negative) spin length
$S=\set{N/2,N/2-1,\cdots}$, and a spin projection
$m_\z\in\set{S,S-1,\cdots,-S}$ onto a quantization axis.  To
generalize this classification to SU($n$), we denote the manifold of
states with definite fixed spin length $S$ by $\M_{N/2-S}$.  The PS
manifold of Dicke states with $S=N/2$ is then $\M_0$, the manifold of
single-magnon spin-wave states with $S=N/2-1$ is $\M_1$, and more
generally the manifold of $r$-magnon states with $S=N/2-r$ is $\M_r$.
Rather than the spin projection $m_\z$ we then identify states by
labels $m=\p{m_\up,m_\dn}\in\A_2\p{N}$ in which $m_\mu$ denotes the
occupation number of the single-spin state $\mu$, with
$m_\up+m_\dn=N$ and $m_\up-m_\dn=m_\z$.

\begin{figure}
  \centering
  \includegraphics{structure/mat_L101_a2.pdf}
  \caption{Visualizations of dimension-$r$ tensors $\m w$ that
    generate the lowest-lying (unnormalized) $r$-magnon states
    $\ket{\m w,m} \equiv \O\p{\m w, \sigma_\z^{\otimes{r}}} \ket{m}$
    with definite excitation energy $\Delta$ above the PS manifold
    $\M_0$ in a periodic 1D lattice of $N=101$ spins interacting via
    the SU(2)-symmetric Hamiltonian in \eqref{eq:H_SU2} with power-law
    couplings $h_{ij}=-1/\oper{dist}\p{i,j}^2$.  Here
    $\oper{dist}\p{i,j}\equiv\min\p{\abs{i-j},N-\abs{i-j}}$ is the
    minimal distance between spins $i,j$.  Top row ($r=2$) shows the
    full 2D matrix $\m w = \sum_{i,j}w_{ij}\op{i}{j}$, and bottom row
    ($r=3$) shows a single 2D slice of the full 3D tensor,
    $\tilde{\m w}_0 = \sum_{i,j}w_{ij,0}\op{i}{j}$.  Blue (red) pixels
    correspond to matrix elements with a positive (negative) sign, and
    darker colors indicate larger absolute values.  In the case of
    $r=2$, translational invariance enforces $w_{ij}=w_{i-d,j-d}$ for
    all displacements $d$, so every row of $\m w$ is some translation
    of a single (arbitrary) row.  Similarly, when $r=3$ every 2D slice
    of the full 3D tensor can be obtained by appropriately translating
    the 2D slice $\tilde{\m w}_0$ shown above.  In the case of SU($n$)
    with $n>2$, the ``$r$-magnon'' excitation energies $\Delta$ and
    tensors $\m w$ remain identical, but now correspond to a
    degenerate set of states that are generated by different choices
    of $r$-body operators in place of $\sigma_\z^{\otimes r}$.}
  \label{fig:structure}
\end{figure}

@@

The label $m$ suffices to identify the PS (Dicke) manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_2\p{N}}$, but we need additional
labels to uniquely identify states in the $r$-magnon manifold $\M_r$
with $r>0$.  Single-magnon ($r=1$) spin-wave states of SU(2) spin
systems can be written in the form
\begin{align}
  \ket{m,\m v} \equiv \O\p{\m v,\sigma_\z} \ket{m}
  = \sum_j v_j \sigma_\z^{(j)} \ket{m},
\end{align}
where each $v_j$ is a scalar and $\sigma_\z$ is a Pauli-$z$ operator.
If an SU(2) spin system is translationally invariant, then these
spin-wave eigenstates have $v_j=e^{\i k_{\m v}\c j}$ with wavenumber
$k_{\m v}\ne0$.  Similarly, $r$-magnon states for SU(2) take the form
$\ket{m,\m w}\equiv\O\p{\m w,\sigma_\z^{\otimes r}}\ket{m}$, where now
$\m w$ is an $r$-index tensor that encodes the structure of
correlations in the excited state $\ket{m,\m w}$ (see Figure
\ref{fig:structure}).  Considering states of this form, built using
tensor products of Pauli-$z$ ($\sigma_\z$) operators, suffices to
construct a basis for all excited states of an SU(2) spin system (see
Appendix \ref{sec:operator_content}).  Note that $r$-body operators
with arbitrary coefficients $\m w$ will generally couple the PS
manifold $\M_0$ to all $q$-magnon manifolds $\M_q$ with $q\le r$ (see
Figure \ref{fig:manifold_sketch}).  In order to generalize the notion
of $r$-magnon manifolds $\M_r$ to the case of SU($n$) with $n>2$,
where the analogous notion of a spin length $S$ is less intuitive, we
therefore define $\M_r$ for $r>0$ as the manifold of states that (i)
can be generated by the action of $r$-body operators on $\M_0$, and
(ii) are orthogonal to all states in $\bigoplus_{q<r}\M_q$.

@@

In the case of an SU($n$) spin system, we can similarly start with the
ground-state PS manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_n\p{N}}$, and generate excited
states by the action of multi-body operators, $\O\p{\m w,X}\ket{m}$.
The choice of tensors $\m w$ for generating states in the $r$-magnon
manifold $\M_r$ is the same as before, but we now have the additional
complication of having to choose $r$-spin operators, $X$.  As with the
choice of $\sigma_\z^{\otimes r}$ for SU(2), it suffices to choose
tensor products of {\it diagonal} single-spin operators (that is,
diagonal in a fixed single-particle basis), but there will now be
$\sim\p{n-1}^r$ choices: one of $n-1$ diagonal operators (that are
linearly independent of the identity) for each of $r$ tensor factors.
We discuss the exact choice of operators in more detail in Appendix
\ref{sec:operator_content}.  To summarize, we define $n$ single-spin
operators $Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$, for
which $Z_\nu=\pm\sigma_\z$ in the case of SU(2), and we choose a list
of non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with
$\sum_\nu z_\nu=r$ to define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_{\nu=1}^n Z_\nu^{\otimes z_\nu}
  = \underbrace{Z_1 \otimes \cdots \otimes Z_1}_{z_1~\t{times}}
  \otimes
  \underbrace{Z_2 \otimes \cdots \otimes Z_2}_{z_2~\t{times}}
  \otimes \cdots \otimes
  \underbrace{Z_n \otimes \cdots \otimes Z_n}_{z_n~\t{times}}.
\end{align}
Our starting basis for $\M_r$ then consists of states
$\ket{m,\m w,X_z}\equiv\O\p{\m w,X_z}\ket{m}$, where we enforce that
$z_\nu\le m_\nu$ for all $\nu$ (where $m_\nu$ is the occupation number
of the single-spin state $\nu$), and that $z$ is zero in an entry
where $m$ is maximal: $z_\nu=0$ for
$\nu=\min\set{\mu:m_\mu=\max\p{m}}$.  This second restriction is
equivalent to removing an operator from $\set{Z_\nu:\nu\in\ZZ_n}$,
making the remaining set linearly independent of the identity
operator.  The basis $\set{\ket{m,\m w,X_z}}$ for $\M_r$ is generally
complete, but not orthonormal, so as a final step we use the states
$\ket{m,\m w,X_z}$ to (numerically) construct an orthonormal basis
$\B_r$ for $\M_r$ (see Appendix \ref{sec:operator_content}).

\red{[todo: discuss the use of this basis in numerical simulations]}

@@

\red{[note: the remainder of this section is old, and will be replaced
  entirely]}

By construction, the $M$-body operator $X_{\m w}$ generally couples PS
states in $\M_0$ to asymmetric states in $\col\M_M$.  If the coupling
between $\M_0$ and its complement is weak compared to the spectral gap
$\Delta_{\t{gap}}$ of $H_0$, then we can treat the effect of
$X_{\m w}$ perturbatively and derive an effective Hamiltonian
$H_{\t{eff}}$ on $\M_0$.  This ground-state perturbation theory
formally breaks down when the operator norm
$\norm{X_{\m w}}\ge\Delta_{\t{gap}}/2$, in which case the operator
$X_{\m w}$ first couples $\M_0$ to $\col\M_M$, then $\col\M_M$ to
$\col\M_{2M}$, and so on.  Even if
$\norm{X_{\m w}}>\Delta_{\t{gap}}/2$, however, the energetic penalty
incurred by $H_0$ from breaking the permutational symmetry of an
initial state $\ket\psi\in\M_0$ suppresses the leakage of population
into manifolds $\M_r$ of increasing $r$.  One might therefore capture
the dynamics of an initial PS state $\ket\psi\in\M_0$ by projecting
$X_{\m w}$ onto $\col\M_{r_{\t{max}}}$ for some $r_{\t{max}}\ge M$,
resulting in a theory that resembles first-order perturbation theory
on $\col\M_{r_{\t{max}}}$.  In the perturbative regime
$\norm{X_{\m w}}<\Delta_{\t{gap}}/2$, such a theory captures all
virtual processes through order $2\floor{r_{\t{max}}/M}+1$ in a formal
perturbation theory on $\M_0$.  In the non-perturbative regime
$\norm{X_{\m w}}\ge\Delta_{\t{gap}}/2$, the error incurred by
truncating the Hilbert space of a spin system past
$\col\M_{r_{\t{max}}}$ is not clear a priori.  Nonetheless,
simulations restricted to $\col\M_{r_{\t{max}}}$ can be benchmarked by
examining the maximum populations within all $\M_r$ for
$r\le r_{\t{max}}$ throughout simulation.  As long as
\begin{enumerate*}
\item these populations fall off with increasing $r$,
\item and the maximal population within large-$r$ manifolds $\M_r$ is
  small,
\end{enumerate*}
one should expect such simulations to faithfully capture (at least
qualitatively) the dynamical behavior of the spin system under
consideration.

In order to project an operator $X_{\m w}$ onto
$\col\M_{r_{\t{max}}}$, we first need to construct a basis for
$\col\M_{r_{\t{max}}}$, and then compute all matrix elements of
$X_{\m w}$ in this basis.  Our strategy will be to first identify a
basis for $\M_0$, and then find, for each $r=1,\cdots,r_{\t{max}}$, a
suitable set of $r$-body operators $\set{O}$ and dimension-$r$ tensors
$\set{\m u}$ for which the states
$\ket{O,\m u,m}\propto O_{\m u}\ket{m}$ form an orthonormal basis for
$\M_r$.  Matrix elements of $X_{\m w}$ with respect to this basis for
$\col\M_{r_{\t{max}}}$ then take the form
\begin{align}
  \bk{O,\m u,\ell|X_{\m w}|Q,\m v,m}
  = \f{\bk{\ell|O_{\m u}^\dag X_{\m w} Q_{\m v}|m}}
  {\sqrt{\bk{\ell|O_{\m u}^\dag O_{\m u}|\ell}
      \bk{m|Q_{\m v}^\dag Q_{\m v}|m}}}.
  \label{eq:matrix_element}
\end{align}
In order to compute these matrix elements, we simplify products of the
form $\P_0 O_{\m u}^\dag X_{\m w} Q_{\m v} \P_0$ and
$\P_0 O_{\m u}^\dag O_{\m u} \P_0$, with $\P_0$ a projector onto
$\M_0$, in Appendix \ref{sec:operator_product}.

Denoting all assignments of $N$ (identical) spins to $n$ (distinct)
states by $\A_n\p{N}$, a suitable basis for $\M_0$ is the set of PS
states $\set{\ket{m}:m\in\A_n\p{N}}$, where $m=\p{m_1,m_2,\cdots,m_n}$
specifies the occupation number $m_\mu$ of each single-spin state
$\mu$.  For consistency with the expression of matrix elements in
\eqref{eq:matrix_element}, for each $\ket{m}\in\M_0$ we define
$\ket{\1,1,m}\equiv\ket{m}$, with $\1$ the identity operator, and we
define $\1_1\equiv\1$.  We now need to determine the set of $r$-body
operators $\set{O}$ and dimension-$r$ tensors $\set{\m u}$ that define
our basis for each $\M_r$.  As an initial guess for $\set{\m u}$, we
can choose the set $\set{\m u_\Delta}_{\m h,r}$ of dimension-$r$
tensors $\m u_\Delta$ that generate eigenstates of $H_0$.  The set of
$r$-body operators to choose is less obvious, but can be determined by
an exhaustive search over all $r$-body operators relevant to a
particular scenario.  Specifically, the purpose of projecting
operators onto $\col\M_{r_{\t{max}}}$ is to simulate the dynamics
induced by some operator $\hat\O$ of the form in \eqref{eq:pert},
constructed from a set $\O=\set{\p{X,\m w}}$ containing multi-spin
operators $X$.  In order to find a basis for the {\it relevant} states
in $\M_r$, one can simply consider the set $\set{O}_{\O,r}$ all
$r$-spin operators that can be constructed from products of the
multi-spin operators $X$ in $\O$.

In general, the states $\ket{O,\m u_\Delta,m}$ for all
$\p{O,\m u_\Delta,m}\in\set{O}_{\O,r}\times\set{\m u_\Delta}_{\m h,r}
\times\A_n\p{N}$ will form an overcomplete basis for the relevant
states in $\col\M_r$.  Our last step is therefore to reduce this set
of states to a minimal basis $\B_r$ for $\M_r$.  To this end, we
construct each of $\B_1,\B_2,\cdots,\B_{r_{\t{max}}}$ in sequence,
such that when constructing $\B_r$ we already have a minimal basis
$\col\B_{r-1}\equiv\bigcup_{s<r}\B_s$ for $\col\M_{r-1}$.  To
construct $\B_r$, we then consider each
$\p{O,\m u_\Delta,m}\in\set{O}_{\O,r}\times\set{\m u_\Delta}_{\m h,r}
\times\A_n\p{N}$ one at a time.  If $\ket{O,\m u_\Delta,m}$ is
orthogonal to all states in $\col\B_{r-1}$, as well as all other
states we have added to $\B_r$ thus far, then we include it in $\B_r$.
Otherwise, we discard $\ket{O,\m u_\Delta,m}$.  There are two
considerations to keep in mind for this construction: first, one
should always throw out null states $\ket{O,\m u_\Delta,m}=0$, which
can be identified by a vanishing self-overlap,
$\bk{O,\m u_\Delta,m|O,\m u_\Delta,m}=0$.  Second, computing overlaps
to check for orthogonality can be computationally intensive.  When
considering a candidate state $\ket{O,\m u_\Delta,m}$ to add to
$\B_r$, one can therefore restrict orthogonality checks to other
states $\ket{Q,\m v_\epsilon,\ell}$ with $\epsilon=\Delta$; if the
excitation energies $\epsilon\ne\Delta$, then these states are
guaranteed to be orthogonal.  Any two states with different occupation
numbers of single-spin states $\mu\in\ZZ_n$ are similarly guaranteed
to be orthogonal.

\red{[look at \cite{rai1988correlated} for classifying asymmetric
  states?]}

@@

Here we simplify the product
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  &\equiv \O\p{\m u,Z\otimes Z} \O\p{\m v,Z\otimes Z}
  \O\p{\m w,Z\otimes Z} \\
  &= \sum_{i\ne j} \sum_{k\ne\ell} \sum_{p\ne q}
  u_{ij} v_{k\ell} w_{pq} Z_i Z_j Z_k Z_\ell Z_p Z_q,
\end{align}
projected onto the PS manifold $\M_0$, where $i,j,k,\ell,p,q$ index
individual spins; $Z$ is a single-spin Ising-like operator, with
$Z^2=1$; and $\m m\equiv\sum_{i,j} m_{ij}\op{i}{j}$ for
$\m m\in\set{\m u,\m v,\m w}$ are matrices of scalar coefficients,
with $m_{ii}=0$.  This product appears, for example, in the projection
of Ising interactions onto the two-body excitation manifold $\M_2$.
Collecting terms according to the number of $Z$ operators that remain
after accounting for $Z^2=1$, we find that
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS A_6 Z^{\otimes 6} + A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
  \label{eq:triple_multi}
\end{align}
with
\begin{align}
  A_6 \equiv \diagram{triple_0},
  &&
  A_4 \equiv 4 \diagram{triple_01} + 8 \diagram{triple_1},
  &&
  A_0 \equiv 8 \diagram{triple_0111},
  \label{eq:triple_64}
\end{align}
\begin{align}
  A_2 \equiv 8 \diagram{triple_011} + 2 \diagram{triple_02}
  + 8 \diagram{triple_11} + 4 \diagram{triple_2},
  \label{eq:triple_2}
\end{align}
where a diagram with unlabeled circles denotes a sum over all distinct
label assignments, e.g.
\begin{align}
  \diagram{triple_1} \equiv \diagram{triple_1_uvw},
  \label{eq:triple_uvw}
\end{align}
\begin{align}
  \diagram{triple_011}
  \equiv \diagram{triple_011_uvw}
  + \diagram{triple_011_vwu} + \diagram{triple_011_wuv}.
  \label{eq:triple_uvw_3}
\end{align}
The last diagram in each of $A_6,A_4,A_2,A_0$ as written in
\eqref{eq:triple_64}, \eqref{eq:triple_2} thus has only one assignment
of labels, as in \eqref{eq:triple_uvw}, while all other unlabeled
diagrams have three assignments, as in \eqref{eq:triple_uvw_3}.

>>>>

In order to simulate dynamics within excited-state manifolds, we first
need to classify the set of excited states, and construct a suitable
basis.  In the case of SU(2), a common starting point is to identify
states with a definite (non-negative) spin length
$S=\set{N/2,N/2-1,\cdots}$, and a spin projection
$m_\z\in\set{S,S-1,\cdots,-S}$ onto a quantization axis.  To
generalize this classification to SU($n$), we denote the manifold of
states with definite fixed spin length $S$ by $\M_{N/2-S}$.  The PS
manifold of Dicke states with $S=N/2$ is then $\M_0$, the manifold of
single-magnon spin-wave states with $S=N/2-1$ is $\M_1$, and more
generally the manifold of $r$-magnon states with $S=N/2-r$ is $\M_r$.
Rather than the spin projection $m_\z$, we then identify states by
labels $m=\p{m_\up,m_\dn}\in\A_2\p{N}$ in which $m_\mu$ denotes the
occupation number of the single-spin state $\mu$, with $m_\up+m_\dn=N$
and $m_\up-m_\dn=m_\z$.

% \begin{figure}
%   \centering
%   \includegraphics{structure/mat_L101_a2.pdf}
%   \caption{Visualizations of dimension-$r$ tensors $\m w$ that
%     generate the lowest-lying (unnormalized) $r$-magnon states
%     $\ket{\m w,m} \equiv \O\p{\m w, \sigma_\z^{\otimes{r}}} \ket{m}$
%     with definite excitation energy $\Delta$ above the PS manifold
%     $\M_0$ in a periodic 1D lattice of $N=101$ spins interacting via
%     the SU(2)-symmetric Hamiltonian in \eqref{eq:H_SU2} with power-law
%     couplings $h_{ij}=-1/\oper{dist}\p{i,j}^2$.  Here
%     $\oper{dist}\p{i,j}\equiv\min\p{\abs{i-j},N-\abs{i-j}}$ is the
%     minimal distance between spins $i,j$.  Top row ($r=2$) shows the
%     full 2D matrix $\m w = \sum_{i,j}w_{ij}\op{i}{j}$, and bottom row
%     ($r=3$) shows a single 2D slice of the full 3D tensor,
%     $\tilde{\m w}_0 = \sum_{i,j}w_{ij,0}\op{i}{j}$.  Blue (red) pixels
%     correspond to matrix elements with a positive (negative) sign, and
%     darker colors indicate larger absolute values.  In the case of
%     $r=2$, translational invariance enforces $w_{ij}=w_{i-d,j-d}$ for
%     all displacements $d$, so every row of $\m w$ is some translation
%     of a single (arbitrary) row.  Similarly, when $r=3$ every 2D slice
%     of the full 3D tensor can be obtained by appropriately translating
%     the 2D slice $\tilde{\m w}_0$ shown above.  In the case of SU($n$)
%     with $n>2$, the ``$r$-magnon'' excitation energies $\Delta$ and
%     tensors $\m w$ remain identical, but now correspond to a
%     degenerate set of states that are generated by different choices
%     of $r$-body operators in place of $\sigma_\z^{\otimes r}$.}
%   \label{fig:structure}
% \end{figure}

@@

The label $m$ suffices to identify the PS (Dicke) manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_2\p{N}}$, but we need additional
labels to uniquely identify states in the $r$-magnon manifold $\M_r$
with $r>0$.  Single-magnon ($r=1$) spin-wave states of SU(2) spin
systems can be written in the form
\begin{align}
  \ket{m,\m v,\sigma_z}
  \equiv \O\p{\m v,\sigma_\z} \ket{m}
  = \sum_{j=1}^N v_j \sigma_\z^{(j)} \ket{m},
\end{align}
where each $v_j$ is a scalar and $\sigma_\z$ is a Pauli-$z$ operator.
If an SU(2) spin system is translationally invariant, then these
spin-wave eigenstates have $v_j=e^{\i k_{\m v}\c j}$ with wavenumber
$k_{\m v}\ne0$.  Similarly, $r$-magnon states for SU(2) take the form
$\ket{m,\m w,\sigma_\z^{\otimes r}} \equiv \O\p{\m
  w,\sigma_\z^{\otimes r}}\ket{m}$, where now $\m w$ is an $r$-index
tensor that encodes the structure of correlations in the excited state
$\ket{m,\m w,\sigma_\z^{\otimes r}}$.  Considering states of this
form, built using tensor products of Pauli-$z$ ($\sigma_\z$)
operators, suffices to construct a basis for all excited states of an
SU(2) spin system (see Appendix \ref{sec:operator_content}).  Note
that $r$-body operators with arbitrary coefficients $\m w$ will
generally couple the PS manifold $\M_0$ to all $q$-magnon manifolds
$\M_q$ with $q\le r$ (see Figure \ref{fig:manifold_sketch}).  In order
to generalize the notion of $r$-magnon manifolds $\M_r$ to the case of
SU($n$) with $n>2$, where the analogous notion of a spin length $S$ is
less intuitive, we can define $\M_r$ for $r>0$ as the manifold of
states that (i) can be generated by the action of $r$-body operators
on $\M_0$, and (ii) are orthogonal to all states in
$\bigoplus_{q<r}\M_q$.

@@

In the case of an SU($n$) spin system, we can similarly start with the
ground-state PS manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_n\p{N}}$, and generate excited
states by the action of multi-body operators,
$\ket{m,\m w,X}\equiv\O\p{\m w,X}\ket{m}$.  The choice of tensors
$\m w$ for generating states in the $r$-magnon manifold $\M_r$ is the
same as before, but we now have the additional complication of having
to choose $r$-spin operators, $X$.  As with the choice of
$\sigma_\z^{\otimes r}$ for SU(2), it suffices to choose tensor
products of {\it diagonal} single-spin operators (that is, diagonal in
a fixed single-particle basis), but there will now be $\sim\p{n-1}^r$
choices: one of $n-1$ diagonal operators (that are linearly
independent of the identity) for each of $r$ tensor factors.  We
discuss the exact choice of operators in more detail in Appendix
\ref{sec:operator_content}.  To summarize, we define $n$ single-spin
operators $Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$, for
which $Z_\nu=\pm\sigma_\z$ in the case of SU(2), and we choose a list
of non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with
$\sum_\nu z_\nu=r$ to define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_{\nu=1}^n Z_\nu^{\otimes z_\nu}
  = \underbrace{Z_1 \otimes \cdots \otimes Z_1}_{z_1~\t{times}}
  \otimes
  \underbrace{Z_2 \otimes \cdots \otimes Z_2}_{z_2~\t{times}}
  \otimes \cdots \otimes
  \underbrace{Z_n \otimes \cdots \otimes Z_n}_{z_n~\t{times}}.
\end{align}
Our starting basis for $\M_r$ then consists of states
$\ket{m,\m w,X_z}$, where we enforce that $z_\nu\le m_\nu$ for all
$\nu$ (where $m_\nu$ is the occupation number of the single-spin state
$\nu$), and that $z$ is zero in an entry where $m$ is maximal:
$z_\nu=0$ for $\nu=\min\set{\mu:m_\mu=\max\p{m}}$.  This second
restriction is equivalent to removing an operator from
$\set{Z_\nu:\nu\in\ZZ_n}$, making the remaining set linearly
independent of the identity operator.  The basis
$\set{\ket{m,\m w,X_z}}$ for $\M_r$ is generally complete, but not
orthonormal, so as a final step we use the states $\ket{m,\m w,X_z}$
to (numerically) construct an orthonormal basis $\B_r$ for $\M_r$ (see
Appendix \ref{sec:operator_content}).

By repeating the above process incrementally for all
$r\le r_{\t{max}}$ (starting with $r=1$), we can construct an
orthonormal basis
$\col\B_{r_{\t{max}}}\equiv\bigotimes_{r\le r_{\t{max}}}\B_r$ for the
combined manifold of all states with at most $r_{\t{max}}$ magnons,
$\col\M_{r_{\t{max}}}\equiv\bigotimes_{r\le r_{\t{max}}}\M_r$.  The
purpose of constructing the basis $\col\B_{r_{\t{max}}}$ is to
simulate the dynamics induced by the addition of a spin operator
$\O\p{\m v,Y}$ to the base Hamilonian $H_0$, such that the total
Hamiltonian is $H = H_0 + \O\p{\m v,Y}$.  Throughout the construction
of $\col\B_s$, an appropriate choice of tensors $\m w$ ensures that
all states $\ket{m,\m w,X}\in\col\B_s$ are eigenstates of the base
Hamiltonian $H_0$ (see Appendix \ref{sec:eigenstates}), which is to
say that $H_0$ is diagonal with respect to $\col\B_s$.  Matrix
elements of $\O\p{\m v,Y}$, meanwhile, take the form
\begin{align}
  \bk{\ell,\m u,X|\O\p{\m v,Y}|m,\m w,Z}
  = \bk{\ell|\O\p{\m u,X}\O\p{\m v,Y}\O\p{\m w,Z}|m}.
\end{align}
In order to compute these matrix elements, we simplify general
products of multi-body operators in Appendix
\ref{sec:operator_product}.  For brevity, we will refer to numerical
simulations restricted to $\col\M_{r_{\t{max}}}$ as {\it
  order-$r_{\t{max}}$ truncated shell} (TS$_{r_{\t{max}}}$)
simulations.

An $M$-spin operator $\O\p{\m v,Y}$ can only couple $r$-magnon states
to $q$-magnon states with $\abs{q-r}\le M$.  In the perturbative
regime, $\norm{\O\p{\m v,Y}}<\Delta_{\t{gap}}/2$, TS$_{r_{\t{max}}}$
simulations of initially PS (zero-magnon) states therefore capture all
virtual processes through order $2\floor{r_{\t{max}}/M}+1$ in
perturbation theory.  When $\norm{\O\p{\m v,Y}}\ge\Delta_{\t{gap}}/2$,
perturbation theory formally breaks down, and the error incurred by
neglecting all $s$-magnon states with $s>r_{\t{max}}$ is not clear a
priori.  Nonetheless, TS$_{r_{\t{max}}}$ simulations can be
benchmarked by examining the populations of all $r$-magnon manifolds
$\M_r$ with $r\le r_{\t{max}}$.  As long as the maximal populations
within large-$r$ manifolds $\M_r$ are small, one should expect these
simulations to faithfully capture (at least qualitatively) the
dynamical behavior of the spin system under consideration.

@@

@@

Here we simplify the product
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  &\equiv \O\p{\m u,Z\otimes Z} \O\p{\m v,Z\otimes Z}
  \O\p{\m w,Z\otimes Z} \\
  &= \sum_{i\ne j} \sum_{k\ne\ell} \sum_{p\ne q}
  u_{ij} v_{k\ell} w_{pq} Z_i Z_j Z_k Z_\ell Z_p Z_q,
\end{align}
projected onto the PS manifold $\M_0$, where $i,j,k,\ell,p,q$ index
individual spins; $Z$ is a single-spin Ising-like operator, with
$Z^2=1$; and $\m m\equiv\sum_{i,j} m_{ij}\op{i}{j}$ for
$\m m\in\set{\m u,\m v,\m w}$ are matrices of scalar coefficients,
with $m_{ii}=0$.  This product appears, for example, in the projection
of Ising interactions onto the two-magnon manifold $\M_2$.  Collecting
terms according to the number of $Z$ operators that remain after
accounting for $Z^2=1$, we find that
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS A_6 Z^{\otimes 6} + A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
  \label{eq:triple_multi}
\end{align}
with
\begin{align}
  A_6 \equiv \diagram{triple_0},
  &&
  A_4 \equiv 4 \diagram{triple_01} + 8 \diagram{triple_1},
  &&
  A_0 \equiv 8 \diagram{triple_0111},
  \label{eq:triple_64}
\end{align}
\begin{align}
  A_2 \equiv 8 \diagram{triple_011} + 2 \diagram{triple_02}
  + 8 \diagram{triple_11} + 4 \diagram{triple_2},
  \label{eq:triple_2}
\end{align}
where a diagram with unlabeled circles denotes a sum over all distinct
label assignments, e.g.
\begin{align}
  \diagram{triple_1} \equiv \diagram{triple_1_uvw},
  \label{eq:triple_uvw}
\end{align}
\begin{align}
  \diagram{triple_011}
  \equiv \diagram{triple_011_uvw}
  + \diagram{triple_011_vwu} + \diagram{triple_011_wuv}.
  \label{eq:triple_uvw_3}
\end{align}
The last diagram in each of $A_6,A_4,A_2,A_0$ as written in
\eqref{eq:triple_64}, \eqref{eq:triple_2} thus has only one assignment
of labels, as in \eqref{eq:triple_uvw}, while all other unlabeled
diagrams have three assignments, as in \eqref{eq:triple_uvw_3}.
